\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{5pt} % removes footskip warning
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Eduardo} \Large Mendoza&
  \href{mailto:edumendozamz@gmail.com}{\underline{edumendozamz@gmail.com}}\\
  \href{https://github.com/edoomm/}{\underline{github.com/edoomm}} $|$
  \href{https://www.linkedin.com/in/eduardomen/}{\underline{linkedin.com/in/eduardomen}}& 
  \href{https://t.me/edoomm}{\underline{+52 56 1984 9863}} $|$
  \href{https://signal.me/#eu/nbA8MEeVAIQwuBKdaSnOWAL3wR6m5Nv94BrAf6w9k9nt3ng1mH9AxZpR8t-L9YTl}
  {\underline{+49 1575 3518714}}\\
\end{tabular*}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      
    \resumeSubheading
      {\href{https://drive.google.com/file/d/1b7q_iYOFrz2O6aD8oYceCrmyr7THQtph/view}
      {\underline{Software Developer}}}
      {Apr 2022 -- Jul 2022, May 2024 -- Present}
      {Quad}{Sussex, USA}
      \resumeItemListStart
        \resumeItem{Develop back end (services, APIs, tests) in C\#, front end User Interfaces
        in Javascript/Typescript (react, jQuery, ajax) and database management through Oracle and
        Mongo databases.}
        \resumeItem{Be part of a scrum IT team that gives more control over printing scheduling
        information to business users innovating processes, analyzing system improvement requests and estimating development times.}
    \resumeItemListEnd

    \resumeSubheading
      {\href{https://drive.google.com/file/d/1Bxfeqdok2fCH01pifJdr1nXX4X0KZXNO/view}
      {\underline{Software Engineer Intern}}}
      {Feb 2023 -- Jul 2023}
      {Audi AG}{Ingolstadt, Germany}
      \resumeItemListStart
        \resumeItem{Worked on a project focused on adaptive learning for the future self-driving
        car users.}
        \resumeItem{Implemented Python modules to control car settings: LEDs, seat
        positions, HMI layouts, Bluetooth connection.}
        \resumeItem{Ran, tested and improved scripts directly on a car, which enabled faster
        deliverables and quality assurance.}
        \resumeItem{Championed best Python (documentation, code style) and Git practices that gave
        the project a solid structure.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://drive.google.com/file/d/1cO-Yvrp6AO9TWqM_uM_jAB38-qxkqhqL/view}
      {\underline{Software Engineer Intern}}}
      {Aug 2018 -- Apr 2021}
      {ENCB - IPN}{Mexico City}
      \resumeItemListStart
        \resumeItem{Directed a \href{https://github.com/evaseac/}{\underline{react native
        project}} that helped rural communities evaluate aquatic ecosystems with interactive and
        user-friendly forms that performed evaluations and gave insights about the health of these
        ecosystems.}
        \resumeItem{Created a web page that compiled years of investigation and data used for
        laboratory
        experimentation.}
        \resumeItem{Facilitated a C\# desktop app that managed information and provided features
        to manage the web page.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Göttingen -- Applied Computer Science
      \href{https://drive.google.com/file/d/1QkxxSF2UivDVq-MZCiQvfi-PsIWIwf4Q/view}
      {\underline{(2.1 GPA)}}}
      {Göttingen, Germany}
      {Year abroad studying topics related to AI and Data Science.}
      {Oct 2022 -- Sep 2023}
    \resumeSubheading
      {ESCOM - IPN -- Computer Systems Engineering
      (\href{https://drive.google.com/file/d/1SaT7vYaplQK-PwNCmCEnTRZSrFrwz-yK/view}
      {\underline{90 GPA)}}}
      {Mexico City}
      {Specialized in Software Development.}
      {Aug 2018 -- Jun 2022}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects \& Leadership}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://pypi.org/project/stmeasures/}
          {\textbf{\underline{Trajectory Similarity Measures}}} $|$
          \emph{Python, Jupyter, C, C++, Git/Github}}
          {Feb 2024 -- Dec 2024}
          \resumeItemListStart
            \resumeItem{Developed a \href{https://github.com/TT2024-B106/stmeasures}
            {\underline{Python and C library}} for geometrical computation that will enable
            querying similar trajectories based on geospatial data of thousands of mobile devices.}
            \resumeItem{Evaluated best Python/C++ and Python/C integrations using libraries like
            cppyy, ctypes and cython.}
            \resumeItem{Implemented different algorithms and benchmarking with state-of-the-art
            solutions.}
            \resumeItem{Integrated Github Actions for building, testing and deployment of tests
            libraries to \href{https://stmeasures.readthedocs.io/en/latest/}{\underline{Read The
            Docs}} and PyPI.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://drive.google.com/file/d/1EMWTYJzj80dJdlMeuz7X3F-bEpyTPFCr/view}
          {\textbf{\underline{AIESEC - Mexico}}
          \textbf{/ Belgium \& Austria}} --
          \emph{Team Leader / Team Member}}{Feb 2021 -- Jul 2022}
          \resumeItemListStart
            \resumeItem{Reached +1k volunteers and interns to take an opportunity abroad, leading
            us to be top \#1 in Mexico’s office.}
            \resumeItem{Managed teams +10 members to direct the first stage of the sales
            funnel process and carried sales meetings.}
            \resumeItem{Collaborated with people from other countries to receive foreign interns
            and even created \href{https://github.com/edoomm/time-tracker}{\underline{IT
            projects}.}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://drive.google.com/file/d/1b1CNu-eeZlTg1rc_nXvGEXps3hik2itj/view}
          {\underline{SARA}}
          (Warehouse Management System)} $|$
          \emph{Java, PHP, JS, SQL}}
          {Sep 2020 -- Jan 2021}
          \resumeItemListStart
            \resumeItem{Led a team of 8 classmates with a scrum organization to develop an
            \href{https://github.com/edoomm/sistema-picking-app}{\underline{Android}} and a 
            \href{https://github.com/edoomm/sistema-picking-web}{\underline{Web application}.}}
            \resumeItem{Optimized picking process, using camera APIs and interactive screens that
            improved warehouse processes.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming languages}{: Python \& C\# (+2.5 years), C++ \& JS (1.5 years), C \& Java
     \& PHP (1 year).} \\
     \textbf{Other technologies/tools}{: Azure DevOps, JQuery, Ajax, MySQL, MongoDB, Bash, Docker,
     React, Hadoop, Hive, Pytorch, Bootstrap, G Suite, Google Apps Scripts, Neovim, Linux (Arch \&
     Debian), Git, Github, Adobe suite.} \\
     \textbf{Languages}{: English (C1), German (B2), Portuguese (B1), Spanish (native).}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
